Modal Abstractions for Virtualizing Memory Addresses

### 2023-04-13 examples.tex

The wrinkle, and the importance of the modal treatment of assertions, is that the target thread's precondition is \emph{relative to its address space}, not the address space of the calling thread shown as 
\[[\rtv'+56](\mathcal{I}\texttt{ASpace}(\theta,m) \ast \texttt{Pother})\]
in the specfication. \todo[Colin: could you associate the rest of this paragraph with spec?]Thus the precondition of this code is that the then-current stack pointer has a return address expecting the then-current callee-save register values and suitablly updated (i.e., post-return) stack in the \emph{current} (initial) address space, while the stack pointer saved in the context to restore expects the same of the saved registers and stack \emph{in the other address space}. And the postcondition is analagous, but interpreted \emph{in a different address space}: the then-current (updated) stack has a return address expecting the new (restored) register values, and the saved context's invariant captures the precondition for restoring its execution \emph{in the previous address space}. At that point, it is safe to execute a return (or in a variant on this for user-mode and/or preemptive scheduling, a return-from-interrupt instruction).

>>>>

The wrinkle, and the importance of the modal treatment of assertions, is that the target thread's precondition is \emph{relative to its address space}, not the address space of the calling thread shown as 
\[[\rtv'+56](\mathcal{I}\texttt{ASpace}(\theta,m) \ast \texttt{Pother})\]
in the specfication. \todo{Colin: could you associate the rest of this paragraph with spec?}Thus the precondition of this code is that the then-current stack pointer has a return address expecting the then-current callee-save register values and suitablly updated (i.e., post-return) stack in the \emph{current} (initial) address space, while the stack pointer saved in the context to restore expects the same of the saved registers and stack \emph{in the other address space}. And the postcondition is analagous, but interpreted \emph{in a different address space}: the then-current (updated) stack has a return address expecting the new (restored) register values, and the saved context's invariant captures the precondition for restoring its execution \emph{in the previous address space}. At that point, it is safe to execute a return (or in a variant on this for user-mode and/or preemptive scheduling, a return-from-interrupt instruction).
